---
title: "Bank Marketing Campaign"
author: "Soane Mota"
date: "June 15, 2019"
output: html_document
---

## Import libraries
```{r Load libraries, message=FALSE, warning=FALSE}
library(tidyverse)
```

# Load Dataset
```{r Load dataset ,message=FALSE}
df <- read_csv("bank.csv")
```


```{r, message=FALSE}
dim(df)
```

```{r, message=FALSE}
head(df)
```

```{r, , message=FALSE}
summary(df)
```
# How to extract unique classes/levels
```{r}
df$poutcome<- factor(df$poutcome)
#unique(df$marital) # view of the unique classes
levels(df$poutcome)
```

```{r}
table(df$poutcome)
```

# Subset dataset
```{r}
# based on variable values
subset <- df[which(df$poutcome=='failure' | df$poutcome == "success"), ]
subset$poutcome<- factor(subset$poutcome)
dim(subset)
```

```{r}
head(subset)
```

```{r}
table(subset$poutcome)
```

# What is the success ratio of the campaign?
```{r}
total_success <- sum(subset$poutcome == "success")
total_failure <- sum(subset$poutcome == "failure")

M1 <- total_success /(total_success + total_failure)
M2 <- total_success /total_failure
```

```{r}
M1
``` 
```{r}
M2
``` 

# Meeting #10

# Age distribution
```{r}
barfill <- "#4293ae"
barlines <- "#1F3552"


p1 <- ggplot(df, aes(x = age)) +
        geom_histogram(aes(y = ..count..), binwidth = 5,
                       colour = barlines, fill = barfill) +
        scale_x_continuous(name = "Mean ozone in\nparts per billion",
                           breaks = seq(0, 175, 25),
                           limits=c(0, 175)) +
        scale_y_continuous(name = "Count") +
        ggtitle("Frequency histogram of mean ozone")
p1

```
#Age distribution according to the marriage status 

# Age distribution according to the marriage status from customers  defaulted before.

#Marital status in the dataset

# Marital response

# Education

# Education response

# Call duration 

# Month distribution

# Month response

# Job

# Job response


# Loan 

# Loan response


# Housing

# Housing distribution
